Turbulence in compact to giant H~II regions

### 2022-12-14 strucfunc_paper.tex
Slightly expand the conclusions

We have used the second-order structure function of velocity centroids
on the plane of the sky to carry out a systematic study of the turbulent kinematics
in a sample of 9 \hii{} regions spanning a wide range of luminosities and sizes.
Our principal findings are as follows:
\begin{enumerate}[1.]
\item The velocity fluctuations range from subsonic (Mach number \(\Mach \approx 0.5\))
  in the case of low-luminosity Galactic regions, such as the Orion Nebula,
  up to supersonic (\(\Mach \approx 2.5\)) in the case of giant extragalactic regions
  such as 30~Doradus in the Large Magellanic Cloud. 
\item The correlation length of the velocity fluctuations is always a small fraction
  (roughly 2\%) of the \hii{} region diameter, implying that turbulent energy
  is injected on scales smaller than about 10\% of the size of each region.
\item The power law slope of the structure function at scales smaller than
  the correlation length is \(m \approx 1 \pm 0.2\) for all regions,
  with no significant correlation with size, luminosity, or velocity amplitude.
  This can be explained as due to a fortuitous cancellation
  between, on the one hand, a steepening underlying velocity spectrum and,
  on the other hand, a reduced role for projection smoothing as the turbulent fluctuations
  pass from the subsonic to the supersonic regime. 
\item The non-thermal component of the emission line widths (\(\sigma\los\)) is found
  to be proportional to the amplitude of the plane-of-sky velocity centroid fluctuations
  (\(\sigma\pos\)) with a slope of unity, but an offset such that
  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\).
  This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
  such as radial expansion, which leave no imprint on \(\sigma\pos\),
  implying that \(\sigma\pos\) is a better diagnostic of turbulent fluctuations than
  \(\sigma\los\), even though it is more challenging to measure.
\item On scales larger than the correlation length, a variety of behaviors are seen.
  Some regions, such as Carina and Hubble~X show uncorrelated homogeneous fluctuations
  at the largest scales, whereas others, such as Orion and 30~Doradus show evidence
  for large-scale gradients in the amplitude of the velocity fluctuations
  with more vigorous turbulence in the core of the nebula than in the outskirts.
  In other regions, such as the Lagoon Nebula and NGC~346, there is evidence
  for quasi-periodic oscillations on scales similar to the size
  of the mapped region. 
\end{enumerate}

>>>>

We have used the second-order structure function of velocity centroids
on the plane of the sky to carry out a systematic study of the turbulent kinematics
in a sample of 9 \hii{} regions spanning a wide range of luminosities and sizes.
Our principal findings are as follows:
\begin{enumerate}[1.]
\item The velocity fluctuations range from subsonic (Mach number \(\Mach \approx 0.5\))
  in the case of low-luminosity Galactic regions, such as the Orion Nebula,
  up to supersonic (\(\Mach \approx 2.5\)) in the case of giant extragalactic regions
  such as 30~Doradus in the Large Magellanic Cloud. 
\item The correlation length of the velocity fluctuations is always a small fraction
  (roughly 2\%) of the \hii{} region diameter (section~\ref{sec:D-vs-r0}),
  implying that turbulent energy
  is injected on scales smaller than about 10\% of the size of each region.
\item The power law slope of the structure function at scales smaller than
  the correlation length is \(m \approx 1.0 \pm 0.2\) for all regions,
  with no significant correlation with size, luminosity, or velocity amplitude
  (section~\ref{sec:constancy-power-law}).
  This can be explained as due to a fortuitous cancellation
  between, on the one hand, a steepening underlying velocity spectrum and,
  on the other hand, a reduced role for projection smoothing as the turbulent fluctuations
  pass from the subsonic to the supersonic regime. 
\item The non-thermal component of the emission line widths (\(\sigma\los\)) is found
  to be proportional to the amplitude of the plane-of-sky velocity centroid fluctuations
  (\(\sigma\pos\)) with a slope of unity, but an offset such that
  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\)
  (section~\ref{sec:sigmapos-vs-sigmalos}).
  This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
  such as radial expansion, which leave no imprint on \(\sigma\pos\),
  implying that \(\sigma\pos\) is a better diagnostic of turbulent fluctuations than
  \(\sigma\los\), even though it is more challenging to measure.
\item The amplitudes of \ha{} surface brightness fluctuations
  and turbulent velocity fluctuations 
  are only weakly correlated (Figure~\ref{fig:brightness-pdfs}h).
  For regions with supersonic turbulence
  these are consistent with the
  predictions for turbulence-induced density fluctuations,
  but for regions with subsonic turbulence the inferred density fluctuations
  are too large to be caused by turbulence alone. 
\item On scales much larger than the correlation length,
  a variety of behaviors are seen (section~\ref{sec:evid-inhom-at}).
  Some regions, such as Carina and Hubble~X show uncorrelated homogeneous fluctuations
  at the largest scales, whereas others, such as Orion and 30~Doradus show evidence
  for radial gradients in the amplitude of the velocity fluctuations
  with more vigorous turbulence in the core of the nebula than in the outskirts.
  In other regions, such as the Lagoon Nebula and NGC~346, there is evidence
  for quasi-periodic oscillations on scales similar to the size
  of the mapped region. 
\end{enumerate}
